Put Title here

### 2018-11-24 General WLD combinatorics.tex
put my changes back

\begin{lem}\label{lem sian 1}
  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
    \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
      \begin{enumerate}
        \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2)$.\label{item lonely 2}
        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
        \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
      \end{enumerate}
  \end{enumerate}
\end{lem}

@@

\begin{enumerate}
  \item $S_0={p}$ and $T_0$ is the support of $p$ except for $n$.  Set $i=0$.
  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \sup (\text{supp}(R) - \{n\})$.\label{item loop step}
  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not yet been assigned then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.  Do so, removing $q_{i+1}$'s old assignment.  This frees up a vertex $v_{i}$ in $T_i$ and so there is a propagator $q_{i} \in S_{i}$ which can be assigned to this vertex freeing up an earlier vertex and so on until $p$ has been assigned.  This new assignment contradicts the maximality of $f$.
  \item  If nothing changed in step \ref{item loop step} then all vertices of $T_{i+1}$ are assigned to propagators in $S_{i+1}-\{p\}$ and vice versa.  Thus $|S_{i+1}| = |T_{i+1}|+1$.  Also all the support of propagators in $S_{i+1}$ is in $T_{i+1} \cup \{n\}$, which is a set of size $|T_{i+1}|+1 = |S_{i+1}|$.  Thus we have $|S_{i+1}|$ propagators supported on $|S_{i+1}|$ vertices contradicting admissibility.
  \item Increment $i$ and go to \label{itemp loop step}
\end{enumerate}

>>>>

\begin{lem}\label{lem sian 1}
  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
    \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
      \begin{enumerate}
        \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2$.\label{item lonely 2}
        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
        \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
      \end{enumerate}
  \end{enumerate}
\end{lem}

@@

\begin{enumerate}
  \item $S_0={p}$ and $T_0$ is the support of $p$ except for $n$.  Set $i=0$.
  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \sup (\text{supp}(R) - \{n\})$.\label{item loop step}
  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not yet been assigned then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.  Do so, removing $q_{i+1}$'s old assignment.  This frees up a vertex $v_{i}$ in $T_i$ and so there is a propagator $q_{i} \in S_{i}$ which can be assigned to this vertex freeing up an earlier vertex and so on until $p$ has been assigned.  This new assignment contradicts the maximality of $f$.
  \item  If nothing changed in step \ref{item loop step} then all vertices of $T_{i+1}$ are assigned to propagators in $S_{i+1}-\{p\}$ and vice versa.  Thus $|S_{i+1}| = |T_{i+1}|+1$.  Also all the support of propagators in $S_{i+1}$ is in $T_{i+1} \cup \{n\}$, which is a set of size $|T_{i+1}|+1 = |S_{i+1}|$.  Thus we have $|S_{i+1}|$ propagators supported on $|S_{i+1}|$ vertices contradicting admissibility.
  \item Increment $i$ and go to \ref{item loop step}
\end{enumerate}
